\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[margin=0.5in]{geometry}

% Modern hyperlink setup: Dark Blue links, no ugly boxes
\usepackage[colorlinks=true, linkcolor=MidnightBlue, urlcolor=MidnightBlue]{hyperref}

% Font options
\usepackage[T1]{fontenc}
% \usepackage{mathptmx}
% \usepackage{roboto}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[4]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={\raisebox{0.2\height}{\tiny$\bullet$}}, itemsep=0pt, topsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt, topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textbf{KIRTAN JAIN}} \\ \vspace{3pt}
    \small
    \href{tel:6360357636}{\raisebox{0.1\height}\faPhone\ 6360357636} ~ \textbullet ~
    \href{mailto:kirtanjain0504@gmail.com}{\raisebox{0.2\height}\faEnvelope\ kirtanjain0504@gmail.com} ~ \textbullet ~
    \href{https://www.linkedin.com/in/kirtan-jain-19ba55223/}{\raisebox{0.2\height}\faLinkedin\ linkedin.com/kirtan-jain}
    \vspace{-5pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, Patna}{2021 -- 2025}
      {B.Tech in Computer Science and Technology}{CPI: \textbf{7.52}/10}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart\resumeSubheading
      {Samsung Research Institute - Noida}{Jul 2025 -- Present}
      {R\&D Engineer}{Noida, India}
      \resumeItemListStart
        \resumeItem{Developed new features for \textbf{Samsung DeX} and enhanced core \textbf{WindowManager} components, specifically \textbf{freeform windows} and \textbf{split-screen} multitasking, for OneUI 8.5 \& 9.0.}
        \resumeItem{Maintained system stability across \textbf{various form factors} (including foldables) while ensuring seamless integration of AOSP code updates and security patches.}
        \resumeItem{Ensured compliance with Google's \textbf{CTS} and \textbf{Unit Test} standards to validate framework integrity for \textbf{GMS certification}, facilitating secure \textbf{FOTA releases} to global markets.}
      \resumeItemListEnd

    \resumeSubheading
      {Sprinklr}{May 2024 -- Jul 2024}
      {Product Engineering Intern}{Gurgaon, India}
      \resumeItemListStart
        \resumeItem{Architected a middleware solution with a \textbf{custom control UI} to capture and mock GraphQL/REST API responses, effectively slashing local development latency by \textbf{50\%}.}
        \resumeItem{Ensured continuous frontend productivity during backend outages by converting this caching mechanism into a reusable \href{https://www.npmjs.com/package/always-up}{\textbf{npm package}}, now adopted across multiple development environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
  {\textbf{OneIITP} $|$ \emph{React Native}}{\href{https://apps.apple.com/in/app/oneiitp/id6742688561}{App Store} | \href{https://play.google.com/store/apps/details?id=com.oneiitp.app}{Play Store}}
  {\textit{Lead Developer}}{Sep 2024 -- May 2025}
  \resumeItemListStart
    \resumeItem{Developed the unified campus companion app for IIT Patna, integrating live bus tracking, marketplace, and event updates into a scalable platform; currently serving \textbf{2000+ active students}.}
    \resumeItem{Built entirely in \textbf{React Native} for a seamless cross-platform experience (Android/iOS) with optimized latency.}
  \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Alloc8 - Room Allocation Portal} $|$ \emph{MERN}}{\href{https://alloc8.in/}{Website}}
      {\textit{Project Lead}} {Apr 2024 -- Jun 2024}
      \resumeItemListStart
        \resumeItem{Conceptualized and led the development of a portal streamlining hostel room allocation for \textbf{3000 students} into 1400 rooms in a matter of \textbf{minutes}; hosted on \textbf{AWS Lightsail} with Caddy load-balancing.}
        \resumeItem{Implemented \textbf{Redis-based distributed locks} to ensure atomic room selection and secure roommate pairing.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Kotlin, Java, C++, Python, SQL (MySQL), Bash, JavaScript} \\
     \textbf{Android Engineering}{: Jetpack Compose, Coroutines, Flow, Android SDK, JUnit, Espresso, Retrofit, Gradle} \\
     \textbf{Tools \& Platforms}{: AWS, Firebase, Redis, Docker, Git, Perforce, Linux, Postman} \\
     \textbf{Other Frameworks}{: React Native, React.js, Node.js, GraphQL} \\
    }}
 \end{itemize}

%-----------PUBLICATIONS-----------
\section{Publications}
\resumeSubHeadingListStart

    \resumeProjectHeading
  {\textbf{When Words Can’t Capture It All: Video-Based User Complaint Generation}}{\href{https://arxiv.org/abs/2509.19952}{arXiv}}
  {\textit{\href{https://cikm2025.org/}{CIKM 2025}} $|$ Seoul, South Korea} {Dec 2024 -- May 2025}
  \resumeItemListStart
      \resumeItem{Defined \textbf{CoD-V} (Complaint Description from Video), a novel multimodal task to automate technical support reporting. Curated \textbf{ComVID}, a benchmark dataset of 1,176 annotated videos.}
      \resumeItem{Achieved state-of-the-art generation performance by fine-tuning a \textbf{VideoLLama2} model integrated with \textbf{MultiModal RAG}, effectively bridging the gap between visual context and textual issue description.}
  \resumeItemListEnd

%     \resumeProjectHeading
%           {\textbf{M3Hop-CoT: Misogynous Meme Identification}}{\href{https://arxiv.org/abs/2410.09220}{arXiv}}
%           {\textit{\href{https://2024.emnlp.org/program/accepted_main_conference/}{EMNLP 2024}}} {Jan 2024 -- May 2024}
%           \resumeItemListStart
% \resumeItem{Proposed \textbf{M3Hop-CoT}, a Chain-of-Thought framework for detecting multimodal hate speech. Engineered a three-hop prompting strategy (Emotion, Target, and Context) to decode implicit misogyny, significantly outperforming unimodal baselines.}
%           \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements/Extracurricular}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{ICPC India Regional Finalist 2024} (Amritapuri); ranked among the top 3 teams at IIT Patna.}
    \resumeItem{\textbf{Competitive Programming:} Expert on Codeforces (Max: 1805, \href{https://codeforces.com/profile/cerelac}{cerelac}) $|$ 4* on CodeChef (Max: 1927, \href{https://www.codechef.com/users/jarsofcandy}{jarsofcandy}).}
    \resumeItem{Awarded \textbf{KVPY Fellowship} (SA-2019, SX-2020) by Dept. of Science and Technology, Govt. of India.}
    \resumeItem{Secured \textbf{AIR 2194} in JEE Advanced 2021 (Top 1.5\% of 150,000+ candidates).}
    \resumeItem{\textbf{General Secretary, Technical} (Student Gymkhana '24-25)}
    \resumeItem{\textbf{Overall Events Head}, Inter-IIT Cultural Meet 7.0}
    \resumeItem{\textbf{National Finalist}, NTPC Electron Quiz '24. $|$ \textbf{General Quiz Finalist}, at Nihilanth '25 (IIM Calcutta)}
  \resumeSubHeadingListEnd

\end{document}
